\documentclass[12pt]{report}
\usepackage[a4paper, width=150mm,top=25mm,bottom=25mm]{geometry}
\usepackage[ngerman,english]{babel}
\usepackage[ddmmyyyy]{datetime}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[rgb,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,fit}
\usetikzlibrary{calc,matrix}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.misc}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{paths.ortho}
% \usepackage[style=authoryear,natbib=true]{biblatex}
\usepackage[natbib=true]{biblatex}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage[section]{placeins}
\pagestyle{fancy}


% Define some pagestyles

\newenvironment{abstractpage}
    {\cleardoublepage\vspace*{\fill}\thispagestyle{empty}}
    {\vfill\cleardoublepage}
\renewenvironment{abstract}[1]
    {\bigskip\selectlanguage{#1}
    \begin{center}\bfseries\abstractname\end{center}}
    {\par\bigskip}

\fancypagestyle{blank}{
    \fancyhead{}
    \fancyfoot{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
}

\fancypagestyle{default}{
    \fancyhead{}
    \fancyhead[RO,LE]{\leftmark}
    \fancyfoot{}
    \fancyfoot[LE,RO]{\thepage}
    \renewcommand{\headrulewidth}{0.4pt}
    \renewcommand{\footrulewidth}{0pt}
}

% Colors

% TikZ Styles
\tikzset{varnode/.style={circle, draw=red!60, fill=red!5, very thick, minimum
size=12mm}}
\tikzset{opnode/.style={circle, draw=grey!60, fill=grey!5, very thick, minimum
size=9mm}}
\tikzset{connectnode/.style={circle, draw=black!60, fill=grey!60 thick, minimum
size=2mm}}
\tikzset{grapharrow/.style={-{>[scale=1]}, thick}}

\newtheorem{definition}{Definition}[section]


% Content starts here
\bibliography{references}

\begin{document}

\onehalfspacing

\thispagestyle{empty}
\pagestyle{blank}

\input{chapters/00_titlepage}

\begin{abstractpage}
    \begin{abstract}{english}
        Outliers are an important topic in statistics and machine learning.
        They can be hard to identify and what constitutes an outlier might even
        be subjective. In recent years, work has been done to use different
        generative models for outliers. This can not only allow one to
        investigate what potential outliers might look like directly, it can
        also be used to improve classification models, as particularly deep
        neural network classifiers using rectified linear units as activations
        have been shown to yield high-confidence predictions even far away from
        the training data. We propose using a normalizing flow to model the
        probability density of the training data and generate outliers by
        sampling from an outlier distribution in latent space. We improve
        interpretability and control over the generated samples by applying
        archetypal analysis to the latent space of the normalizing flow. We
        show how this leads to outliers with varying similarity to the inlier
        data. These outliers can also be used for subsequent tasks such as
        training confidence-calibrated classifiers.
    \end{abstract}
    \begin{abstract}{ngerman}
        Ausrei{\ss}er sind ein wichtiges Problem in der Statistik und maschinellem
        Lernen. Sie sind oft schwer zu identifizieren, und die Entscheidung, ob
        ein Messwert als Ausrei{\ss}er gewertet wird ist meist subjektiv. In den
        letzten Jahren wurden Methoden entwickelt um mit generativen Modellen
        an die Ausrei{\ss}erproblematik heranzugehen. Generative Modelle erlauben
        nicht nur die direkte Untersuchung von Ausrei{\ss}ern, sie können auch
        benutzt werden um Klassifikationsmodelle zu verbessern.
        Klassifikationsmodelle, die auf künstlichen neuronalen Netzen mit
        rectified linear units als Aktivierungsfunktion beruhen, weisen Klassen
        hohe Wahrscheinlichkeit zu, auch wenn Daten fern von den Trainingsdaten
        betrachtet werden. Wir schlagen vor, einen normalizing flow zu
        verwenden um die Wahrscheinlichkeitsverteilung der Trainingsdaten zu
        modellieren und Ausrei{\ss}er zu generieren, indem im Repräsentationsraum
        von einer Ausrei{\ss}erverteilung gezogen wird. Wir zeigen au{\ss}erdem, wie
        die Interpretierbarkeit und Kontrolle der generierten Ausrei{\ss}er
        verbessert werden kann, indem Archetypanalyse im Repräsentationsraum
        angewendet wird. So können Ausrei{\ss}er mit variierbarer Ähnlichkeit zu
        den Trainingsdaten generiert werden. Diese Ausrei{\ss}er können dann für
        weitere Aufgaben genutzt werden, z.B. das Trainieren eines
        Klassifikationsmodells mit kalibrierter Konfidenz.
    \end{abstract}
\end{abstractpage}

\cleardoublepage
\tableofcontents
\thispagestyle{empty}

\cleardoublepage
\pagestyle{default}
\pagenumbering{arabic}

\input{chapters/01_introduction.tex}
\input{chapters/02_background.tex}
\input{chapters/03_methods.tex}
\input{chapters/04_results.tex}
\input{chapters/05_discussion.tex}

\listoffigures
\printbibliography

\cleardoublepage
\input{chapters/deposition.tex}
\thispagestyle{empty}

\end{document}
